Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2024-12-08 main.tex
notes on improved estimates for potential operators

In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) C_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n C_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
%

@@

We analyze the Bogovski\u{\i} potential operator by similar means. 
Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\mia} u(x)$ pointwise by 
\begin{align*}
    \left| \Bogov_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
    .
\end{align*}
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
%     =
%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
%     .
% \end{align*}
% We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
    .
\end{align*}
% Here, $C_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Here we introduce the numerical constant 
\begin{gather}\label{equation:A_Bogov}
    C_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
\end{gather}
which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
In particular, the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$. 
So the convolution of $u$ is taken against an integrable function. 
Young's convolution inequality now implies: 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) C_{\Bogov}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n C_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 
\\

\subsection{Interaction of potentials with the exterior derivative}

More properties of these operators become apparent after a change of variables. 
We write down the full definition of these operators and perform two substitutions.
For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
leading to 
\begin{align*}
    \Poinc_{\mia} u(x) 
    &= 
    \vol(\Omega)^{-1}
    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
    \chi_{\Omega}\left(x+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    \vol(\Omega)^{-1}
    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
    .
\end{align*}
For the Bogovski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
leading to 
\begin{align*}
    \Bogov_{\mia} u(x) 
    &= 
    \vol(\Omega)^{-1}
    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
    \chi_{\Omega}\left(y+t(x-y)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    - 
    \vol(\Omega)^{-1}
    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
    .
\end{align*}
% We first discuss the support properties of this operator. 
% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
% 
Given $a \in \Omega$, we introduce the potentials 
\begin{align*}
    \Poinc_{\mia,a} u(x) 
    &:= 
    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
    ,
    \\
    \Bogov_{\mia,a} u(x) 
    &:= 
    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
    .
\end{align*}
By definition,
\begin{align*}
    \Poinc_{\mia} u(x) 
    =
    \vol(\Omega)^{-1}
    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
    \quad 
    \Bogov_{\mia} u(x) 
    =
    \vol(\Omega)^{-1}
    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
    .
\end{align*}
We study the interaction of these potential operator with the exterior derivative in more detail.
% 
The main arguments are well-known and establishes the exactness of several de~Rham complexes. 
We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.

>>>>

In particular, the integral $\Poinc_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \Omega$
and its magnitude is pointwise dominated by the convolution of $|u|$ against an integrable function.
Young's convolution inequality now implies: 
\begin{align*}
    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) C_{\Poinc}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u \in L^{\infty}\Alt^{\mia}(\Omega)$. 
Since that space is dense in the Lebesgue spaces, a density argument establishes the following: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n C_{\Poinc}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
%

@@

We analyze the Bogovski\u{\i} potential operator by similar means. 
Suppose that $u \in L^{\infty}\Alt^{\mia}(\bbR^{n})$ with $\supp u \subseteq \overline\Omega$ and that $x \in \bbR^{n}$.
First, if $x \notin \Omega$, then the convexity of $\Omega$ implies that $y + t( x - y ) \notin \Omega$ for all $t > 1$. Hence $\calG_{\mia}(x,y) = 0$ and therefore $\Bogov_{\mia} u(x) = 0$ in that case.
Consider now the case $x \in \overline\Omega$. 
We estimate $\Bogov_{\mia} u(x)$ pointwise by 
\begin{align*}
    \left| \Bogov_{\mia} u(x) \right|
    &=
    \left| 
        \int_{\Omega} \calG_{\mia}(x,y) \,(x-y)\lrcorner u(y)\,dy
    \right| 
    \\&\leq 
    \int_{\Omega} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} |x-y|^{\jeza+1-n} |u(y)| \,dy
    \\&\leq 
    \int_{\bbR^{n}} \vol(\Omega)^{-1} \sum_{\jeza=0}^{\mia-1}\tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(x-y) |x-y|^{\jeza+1-n} |u(y)| \,dy
    .
\end{align*}
Using once more the radial integrals discussed above, we compute 
% We recall the radial integrals 
% \begin{align*}
%     \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} dz
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza+1-n} r^{n-1} dr
%     =
%     \vol_{n-1}(S_1) \int_{0}^{\diam(\Omega)} r^{\jeza} dr
%     =
%     \vol_{n-1}(S_1) \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
%     .
% \end{align*}
% We compute 
\begin{align*}
    &
    \int_{\bbR^{n}} \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \chi_{B_{\diam(\Omega)}(0)}(z) |z|^{\jeza+1-n} \,dz
    \\&
    =
    \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \int_{B_{\diam(\Omega)}(0)} |z|^{\jeza+1-n} \,dz
    \\&
    =
    \vol_{n-1}(S_1) \sum_{\jeza=0}^{\mia-1} \tbinom{\mia-1}{\jeza} \frac{ \diam(\Omega)^{n-\jeza} }{n-\jeza} \frac{\diam(\Omega)^{\jeza+1}}{\jeza+1}
    %\\&
    =
    \vol_{n-1}(S_1) \diam(\Omega)^{n+1} \underbrace{ \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) } }_{ =: C_{\Bogov}(n,\mia) \leq 2^{\mia-1}}
    .
\end{align*}
% Here, $C_{\Bogov}(n,\mia)$ is a numerical constant that depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Here we introduce the numerical constant 
\begin{gather}\label{equation:A_Bogov}
    C_{\Bogov}(n,\mia) := \sum_{\jeza=0}^{\mia-1} \frac{ \tbinom{\mia-1}{\jeza} }{ (n-\jeza)(\jeza+1) }, 
\end{gather}
which depends only on $n$ and $\mia$ and which is bounded by $2^{\mia-1}$. 
Similar as above,
the integral $\Bogov_{\mia} u(x)$ is absolutely convergent for any choice of $x \in \bbR^{n}$
and its magnitude is pointwise dominated by the convolution of $|u|$ against an integrable function.
Young's convolution inequality now implies: 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
    &
    \leq 
    \vol_{n-1}(S_1) C_{\Bogov}(n,\mia) \frac{ \diam(\Omega)^{n} }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    \\&
    \leq 
    n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
    \diam(\Omega)
    \| u \|_{L^{p}(\Omega)}
    .
\end{align*}
We have assumed so far that $u$ is essentially bounded.
Since that space is dense in the Lebesgue spaces, a density argument yields: 
for any $1 \leq p \leq \infty$ we have a bounded linear operator 
\begin{gather*}
    \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow L^{p}\Alt^{\mia-1}(\bbR^n).
\end{gather*}
% Its operator norm is bounded by $n C_{\Bogov}(n,\mia) \vol(\Omega)^{-1} \vol_{}(B_{\diam(\Omega)}(0)) \diam(\Omega)$. 
Moreover, $\supp \Bogov_{\mia} u \subseteq \overline\Omega$,
that is, the reconstructed potential has support contained within $\overline\Omega$. 
\\

\color{blue}
\subsection{Interaction of potentials with the exterior derivative}

More properties of these operators become apparent after a change of variables. 
We write down the full definition of these operators and perform two substitutions.
For the Poincar\'e operator, we substitute $a = x + t(y-x)$ and then we substitute $s = (t-1)/t$,
leading to 
\begin{align*}
    \Poinc_{\mia} u(x) 
    &= 
    \vol(\Omega)^{-1}
    \int_{\Omega} \int_{1}^\infty (t-1)^{\mia-1}t^{n-\mia} 
    \chi_{\Omega}\left(x+t(y-x)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    \vol(\Omega)^{-1}
    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
    .
\end{align*}
For the Bogovski\u{\i} operator, we substitute $a = y + t(x-y)$ and then we substitute $s = t/(t-1)$,
leading to 
\begin{align*}
    \Bogov_{\mia} u(x) 
    &= 
    \vol(\Omega)^{-1}
    \int_{\Omega} \int_{1}^\infty (t-1)^{n-\mia}t^{\mia-1} 
    \chi_{\Omega}\left(y+t(x-y)\right) 
    (x-y)\lrcorner u(y) \,dt\,dy 
    \\
    &=
    - 
    \vol(\Omega)^{-1}
    \int_{\bbR^{n}} \chi_{\Omega}(a) \,(x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt\,da
    .
\end{align*}
% We first discuss the support properties of this operator. 
% Suppose that $u \in C^{\infty}\Alt^{\mia-1}(\bbR^n)$ satisfies $\supp u \subseteq \overline\Omega$.
% Then $\Bogov_{\mia} u(x) = 0$ whenever $x \notin \overline\Omega$,
% meaning $\supp \Bogov_{\mia} u \subseteq \overline\Omega$.
% 
Given $a \in \Omega$, we introduce the potentials 
\begin{align*}
    \Poinc_{\mia,a} u(x) 
    &:= 
    (x-a)\lrcorner \int_{0}^{1} t^{\mia-1} u\left(a+t(x-a)\right)\,dt
    ,
    \\
    \Bogov_{\mia,a} u(x) 
    &:= 
    - (x-a)\lrcorner \int_{1}^\infty t^{\mia-1} u\left(a+t(x-a)\right)\,dt
    .
\end{align*}
By definition,
\begin{align*}
    \Poinc_{\mia} u(x) 
    =
    \vol(\Omega)^{-1}
    \int_{\Omega} \Poinc_{\mia,a} u(x) \,da,
    \quad 
    \Bogov_{\mia} u(x) 
    =
    \vol(\Omega)^{-1}
    \int_{\Omega} \Bogov_{\mia,a} u(x) \,da
    .
\end{align*}
On the background of this rewriting, we can establish additional operator norm bounds for the operator norms. 
These do not depend on the eccentricity of the domain.

We begin with the Poincar\'e operator. 
By an application of Jensen's inequality, operator norm estimates, and substitutions, we find 
\begin{align*}
    \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}^{p}
    &
    \leq 
    \diam(\Omega)^{p}
    \vol(\Omega)^{-1}
    \int_{0}^{1} \int_{\Omega} \int_{\Omega} 
    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{0}^{1} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{0}^{1} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{\Omega} 
    |u( z )|^{p}
    \int_{0}^{1} 
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \,dt \,dz 
    .
\end{align*}
\color{red}
A comparable estimate follows for the Bogovski\u{\i} operator with the substitution 
\begin{align*}
    \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}^{p}
    &
    \leq 
    \diam(\Omega)^{p}
    \vol(\Omega)^{-1}
    \int_{1}^{\infty} \int_{\Omega} \int_{\Omega} 
    t^{p(k-1)} |u( a + t(x-a) )|^{p} \,dt \,da \,dx
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{1}^{\infty} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ z \in (1-t) a + t \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{1}^{\infty} 
    \iint\limits_{\substack{ (z,a) \in \Omega \times \Omega \\ a \in \frac{z}{1-t} + \frac{t}{1-t} \Omega } }
    \vol(t\Omega)^{-1}
    t^{p(k-1)} |u( z )|^{p} \,dz \,da \,dt
    \\&
    = 
    \diam(\Omega)^{p}
    \int_{\Omega} 
    |u( z )|^{p}
    \int_{1}^{\infty} 
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \,dt \,dz 
    .
\end{align*}
\color{blue}
We estimate 
\begin{align*}
    \int_{0}^{1}
    \vol\left(\left\{ 
        \Omega \cap ( \tfrac{1}{1-t} z + \tfrac{t}{1-t} \Omega )
    \right\}\right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \ dt
    &
    \leq 
    \int_{0}^{1}
    \min\left( 
        \vol\left(\Omega\right), 
        \vol\left( \tfrac{t}{1-t} \Omega \right) 
    \right)
    \frac{ t^{p(k-1)} }{ \vol(t\Omega) }
    \ dt
    \\&
    \leq 
    \int_{0}^{1}
    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
    t^{p(k-1)} 
    \ dt
    \\&
    \leq 
    \int_{0}^{1}
    \min\left( \tfrac{1}{t^{n}}, \tfrac{1}{(1-t)^n} \right) 
    t^{k-1} 
    \ dt
    .
\end{align*}
We estimate the last integral via the basic observations
\begin{align*}
    \int_{0}^{\frac 1 2} 
    \frac{ t^{k-1} }{ (1-t)^{n} }
    \ dt
    \leq 
    \int_{0}^{\frac 1 2} 
    (1-t)^{-n+k-1}
    \ dt
    =
    \int_{\frac 1 2}^{1} 
    t^{-n+k-1}
    \ dt
    =
    \begin{cases}
        \ln(2)                 & \text{$n=k$}
        \\
        \frac{2^{n-k}-1}{n-k} & \text{otherwise.}
    \end{cases}
\end{align*}

\subsection{Interaction of potentials with the exterior derivative}
\color{black}
We study the interaction of the Poincar\'e and Bogovski\u{\i} operators with the exterior derivative in more detail.
% 
The main arguments are well-known and establish the exactness of several de~Rham complexes. 
We recapitulate these arguments since our variants of the regularized potential operators are not yet included in the published literature.
